\vspace{-1em}\thetitle

### 2009-09-22 paper.tex
...

\vspace{-0.5em}
\section*{Extended Abstract}

@@

From training data we recover estimates, $W^*$ and $P^*$, of the factors in \Equation{mixture-model-matrix}.
To detect the low-rank linear structures, we use Ma~\emph{et~al.}'s algorithm for segmenting multivariate data into subspaces using lossy data coding and compression~\cite{Ma07}.
Then we determine the hull points of each linear structure, using nonnegative matrix factorization (\caps{NMF})~\cite{Lee01,Kim08:anls}:
if $Q_c$ is a sub-matrix of rows in the same structure class, we want to find nonnegative matrices, $W_c$ and $P_c$, such that $Q_c \approx W_c P_c$.
Our reconstructed $P^*$ is a vertical concatenation of these $P_c$ matrices, while $W^*$ is a row-permutation of the direct sum of $W_c$ matrices.
We use Kim and Park's alternating non-negative least squares algorithm~\cite{Kim08:anls} for rapid initial convergence, but refine the result using Lee and Seung's Euclidean algorithm~\cite{Lee01}.
Good prediction performance requires special initialization of the \caps{NMF} algorithms, using new techniques that we lack room to detail here.

@@

Our method does not yield perfect predictions, but the non-deterministic nature of flow behavior implies that it is impossible to achieve perfect prediction.
Moreover, we do not know what the inherent upper limit on prediction quality is:
no prior work provides detailed statistical models of individual flow behaviors, nor does any earlier research attempt to predict individual flow behavior from a few initial packets.
The fact that this technique can accurately predict flow behavior from so few initial packet observations is evidence that our hypothesized mixture model for flow behavior has merit.
With improvements in the algorithms used to recover the model parameters, we are confident that even better prediction accuracy can be achieved.
Furthermore, the same model can be applied to traffic classification from flow behavior, and to generation of realistic synthetic network traffic from collections of trace data.
These applications, however useful, are merely pleasant side effects of the real breakthrough of this work:
a detailed statistical model for individual and network-wide flow behaviors.

\vspace{-0.5em}
\scriptsize
\bibliographystyle{unsrt}
\bibliography{references}

>>>>

\section*{Extended Abstract}

@@

From training data we recover estimates, $W^*$ and $P^*$, of the factors in \Equation{mixture-model-matrix}.
To detect the low-rank linear structures, we use Ma~\emph{et~al.}'s algorithm for segmenting multivariate data into subspaces using lossy data coding and compression~\cite{Ma07}.
Then we determine the hull points of each linear structure using nonnegative matrix factorization (\caps{NMF})~\cite{Lee01,Kim08:anls}:
if $Q_c$ is a sub-matrix of rows in the same structure class, we want to find nonnegative matrices, $W_c$ and $P_c$, such that $Q_c \approx W_c P_c$.
Our reconstructed $P^*$ is a vertical concatenation of these $P_c$ matrices, while $W^*$ is a row-permutation of the direct sum of $W_c$ matrices.
We use Kim and Park's alternating non-negative least squares algorithm~\cite{Kim08:anls} for rapid initial convergence, but refine the result using Lee and Seung's Euclidean algorithm~\cite{Lee01}.
Good prediction performance requires special initialization of the \caps{NMF} algorithms, using new techniques that we lack room to detail here.

@@

Our method does not yield perfect predictions, but the non-deterministic nature of flow behavior implies that it is impossible to achieve perfect prediction.
Moreover, we do not know what the inherent upper limit on prediction quality is:
no prior work provides detailed statistical models of individual flow behaviors, nor does any earlier research attempt to predict individual flow behavior from a few initial packets.
The fact that this technique can accurately predict flow behavior from so few initial packet observations is evidence that our hypothesized mixture model for flow behavior has merit.
With improvements in the algorithms used to recover the model parameters, we are confident that even better prediction accuracy can be achieved.
Furthermore, the same model can be applied to traffic classification from flow behavior, and to generation of realistic synthetic network traffic from collections of trace data.
These applications, however useful, are merely pleasant side effects of the real breakthrough of this work:
a detailed statistical model for individual flow behaviors across whole networks.

\scriptsize
\bibliographystyle{unsrt}
\bibliography{references}
